What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-08 android-stacks.tex
changing and commenting pictures to gain space.

\begin{table}
  \centering
  \begin{tabular}{rp{22em}}
    \hline
    \bfseries{Type of signaler} & \bfseries{Description} \\
    \hline
    \bfseries{android} & When the exception is explicitly thrown by a method defined in Android Platform, in a the JDK library used by it.\\
    \bfseries{app}     & If the exception signaler was explicitly thrown by an application method or in a the JDK library used by it.\\
    \bfseries{libcore} & If the application was signaled by one of the libraries reused by Android Platform (i.e., org.apache.harmony, org.w3c.dom, sun.misc, org.apache.http, org.json, org.xml) besides the JDK. \\
    \bfseries{lib}     & If the exceptions was not defined by any of the elements above.\\
    \bfseries{java}    & If the application signaler and all the methods that composes the exception are defined in a the JDK library method.\\
    \hline
  \end{tabular}
  \caption{Sources of exceptions in Android}
  \label{tab:signalers}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=\hsize]{top_exceptios_android.pdf}
\caption{Top exceptions in Android repositories.}
\label{fig:androidsignaler}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{chart_exceptiontypes.pdf}
\caption{Distribution of Checked and Unchedked exceptions.}
\label{fig:typeroot}
\end{figure}

>>>>

\begin{table}
  \centering
  \begin{tabular}{rp{22em}}
    \hline
    \bfseries{Type of signaler} & \bfseries{Description} \\
    \hline
    \bfseries{android} & If the exception is thrown by a method defined in Android Platform or OS, or in a JDK library used by them.\\
    \bfseries{app}     & If the exception is thrown by an application method or in a  DK library used by it.\\
    \bfseries{libcore} & If the exception is thrown by one of the core libraries reused by Android (i.e., org.apache.harmony, org.w3c.dom, sun.misc, org.apache.http, org.json, org.xml). \\
    \bfseries{lib}     & If the exception is thrown by a method that was not defined by any of the elements above.\\
    \bfseries{java}    & If all methods on the stack trace are JDK library methods.\\
    \hline
  \end{tabular}
  \caption{Sources of exceptions in Android}
  \label{tab:signalers}
\end{table}

@@

%\begin{figure}
%\centering
%\includegraphics[width=\hsize]{top_exceptios_android_new2.pdf}
%\includegraphics[width=\hsize]{top_exceptions_android_new}
%\caption{Top exceptions in Android repositories.}
%\label{fig:androidsignaler}
%\end{figure}

@@

\begin{figure}
\centering
%\includegraphics[width=\hsize]{chart_exceptiontypes.pdf}
\includegraphics[width=\hsize]{exception_types.pdf}
\caption{Distribution of Checked and Unchedked exceptions.}
\label{fig:typeroot}
\end{figure}
